Supplementary Material for Asymmetry paper

### 2020-06-22 Supplementary/Sup_mat.Rmd
Making my way through the to-do list
Still have to sort the intercept free versions of the Rewards and Probability models

```{r setup, include=T, message=F, warning=F, echo= F}
# library 
library(tidybayes)
library(tidyverse)
library(brms)
library(png)
library(grid)
```

@@

```{r HoopSizeFacets, include=T, echo=F, fig.asp = .75, fig.cap = "_Facet plots for the Hoop Size experiment_"}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

First, we will check that our priors are sensible! (i.e., reasonably flat?)

```{r run-model-hoop-size-priors, echo = T, include = T, message = F, warning = F, cache = TRUE}
# run model
Hoop_size_priors <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                        data = model_data,
                        family = "beta",
                        prior = c(set_prior("student_t(3, 0, 1)",
                                            coef = "norm_hoop_pos",
                                            class = "b"),
                                  set_prior("student_t(3,0,1)",
                                            class = "Intercept")),
                        cores = 2,
                        chains = 2,
                        iter = 5000,
                        warmup = 2500,
                        control = list(adapt_delta = .95, max_treedepth = 15),
                        sample_prior = "only")
```

@@

```{r run-model-Hoop-size, include = T, echo = T, message = F, warning = F, cache = TRUE}
# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = c(set_prior("student_t(3, 0, 1)",
                                        coef = "norm_hoop_pos",
                                        class = "b"),
                              set_prior("student_t(3,0,1)",
                                        class = "Intercept")),
                    cores = 2,
                    chains = 2,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))

@@

@@

``` {r PltHoopSize, include = T, echo = F, fig.asp = .45, fig.cap="_Figure on the left shows the Prior predictions. The figure on the right shows the Posterior predictions once the model had been conditioned on the data_"}

gridExtra::grid.arrange(plt_prior_hoopsize, plt_post_hoopsize, ncol = 2)
```
## Experiment 2: Two Throws

@@

source("extract_draws_functions/Two_throw_draws.R")
```

@@

``` {r TwoThrowFacets, include = T, echo = F, fig.asp = .75, fig.cap = "_Facet plots for each participant in the Two Throw experiment_"}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

```{r Two_Throws_Priors_only_model, include = F, echo = T, cache = T}

my_prior <- c(
  set_prior("student_t(4,0,.8)", class = "b", coef = "norm_delta"),
  set_prior("student_t(4,0,.8)", class = "b", coef = "norm_delta:Num_throwsTwoMThrows"),
  set_prior("student_t(4,0,.8)", class = "b", coef = "Num_throwsTwoMThrows"),
  set_prior("student_t(4,0,.8)", class = "Intercept"))

Two_throw_priors <- brm(
  abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = my_prior,
  cores = 1,
  chains = 1,
  iter = 10000,
  warmup = 5000,
  control = list(adapt_delta = .99, max_treedepth = 15),
  sample_prior = "only")
```

```{r PltTwoThrowPriors, include = T, echo = F, fig.asp=.45, fig.cap="_Prior Predictions for the Two Throw Experiment_"}
# get draws 
draws_df <- draw_post_delta(Two_throw_priors, model_data_pos)

priors_plt <- draws_df$Draws_df %>%
  mutate(prop = boot::inv.logit(estimate),
         Dist_type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(prop,colour = Num_throws, fill = Num_throws)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(expression(paste("Normalised ", Delta))) +
  geom_density(kernel = "biweight", alpha = .3) + 
  facet_wrap(~Dist_type) + 
  theme_bw() + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws"))

priors_plt
```

@@

Two_throw_m1 <- brm(
  abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = my_prior, 
  cores = 1,
  chains = 1,
  iter = 10000,
  warmup = 5000,
  control = list(adapt_delta = .99, max_treedepth = 15))

# load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos")
draws <- draw_post_delta(Two_throw_m1, model_data_pos)

@@

fixef(Two_throw_m1)

@@

Does $\hat{R} = 1$? Do we have a good number of effective samples?

If so, we can have a look at the model fit...

```{r PltTwoThrowEstimates, include = T, echo = F, fig.asp=.55, fig.cap="_The top plots show the Posterior distributions for the estimated mean standing position. The bottom plot shows the distribution of estimated difference between the two conditions for three difference distances_"}

# example distributions 
plt_examples <- draws$Plots[1][[1]][["data"]] %>% 
  mutate(Dist_Type = factor(Dist_type, c("Close", "Mid", "Far")),
         Num_Throws = ifelse(Num_throws == "One_throw", "One", "Two")) %>% 
  ggplot(aes(prop, 
             colour = Num_Throws,
             fill = Num_Throws)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  facet_wrap(~Dist_Type) + 
  theme_bw() + 
  scale_x_continuous(expression(Delta)) + 
  coord_cartesian(expand = F) + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws"))

@@

# show this 
gridExtra::grid.arrange(plt_examples, plt_difference)
```

@@

This effect was the strongest for the closest separation which reflects the larger amount of variation in standing position with distance in the Two-throw condition (Figure \@ref(fig:PltTwoThrowEstimates). In general, when in the One-throw condition, participants stood further from the centre (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) than in the the Two-throw condition (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) with P(One-throw > Two_throw|data) = `r paste(P_close$above0*100, "%", sep = "")`.

@@

source("extract_draws_functions/Reward_draws.R")
```

@@

A Bayesian Beta Regression was carried out in order to investigate whether opting for an unequal reward structure in this task would facilitate the use of a more optimal strategy in the _Throwing Task_. The predictors in this model were whether the participant had opted for an _Equal_ or _Unequal_ (Gamble_Type), whether the hoops were _Close_ or _Far_ (dist_type), and the interaction between these. Additionally, random effects of participant were included for all predictors. The predicted value was the normalised standing position, with 0 representing the centre and 1 being next to one of the hoops.  
```{r GamblingPriorsOnly, include = F, echo = T, warning = F, cache = T}
Reward_priors <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type * Gamble_Type|Participant),
                     data = model_data,
                     family = "beta",
                     prior = c(set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "dist_typefar:Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,.5)",
                                         class = "b",
                                         coef = "Gamble_TypeUnequal"),
                               set_prior("student_t(3,0,1)",
                                         class = "Intercept")),
                     chains = 1,
                     iter = 10000,
                     warmup = 5000,
                     sample_prior = "only",
                     control = list(adapt_delta = .99, max_treedepth = 15))
```

@@

```{r RewardModel, include = F, echo = T, warning = F, cache = T}
# run model 
Reward_m1 <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type*Gamble_Type|Participant),
                 data = model_data,
                 family = "beta",
                 prior = c(set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "dist_typefar"),
                           set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "dist_typefar:Gamble_TypeUnequal"),
                           set_prior("student_t(3,0,.5)",
                                     class = "b",
                                     coef = "Gamble_TypeUnequal"),
                           set_prior("student_t(3,0,1)",
                                     class = "Intercept")),
                 chains = 1,
                 iter = 10000,
                 warmup = 5000,
                 control = list(adapt_delta = .99, max_treedepth = 15))

@@

@@

plt_ProbPrior_meDist <- prior_draws %>%
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

>>>>

```{r setup, include=T, message=F, warning=F, echo= F}
# library 
library(tidybayes)
library(tidyverse)
library(brms)
library(png)
library(grid)
library(gridExtra)

# functions 
# function to extract a legend that is shared accross plots
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
```

@@

```{r HoopSizeFacets, include=T, echo=F, fig.width = 10, fig.height = 10, fig.cap = "_Facet plots for the Hoop Size experiment_"}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

For all models, we opted to use priors that were weakly informative. The chosen priors made the weak assumption that there was no effect of the experimental manipulations introduced in this series of experiments.

``` {r HS_Prior, include = T, echo = F}
HS_prior <- c(set_prior("student_t(3, 0, 1)",
                        coef = "norm_hoop_pos",
                        class = "b"),
              set_prior("student_t(3,0,1)",
                        class = "Intercept"))
```

The models themselves looked as follows:

```{r run-model-hoop-size-priors, echo = T, include = T, message = F, warning = F, cache = TRUE}
# run model
Hoop_size_priors <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                        data = model_data,
                        family = "beta",
                        prior = HS_prior,
                        cores = 2,
                        chains = 2,
                        iter = 5000,
                        warmup = 2500,
                        control = list(adapt_delta = .95, max_treedepth = 15),
                        sample_prior = "only")
```

@@

```{r run-model-Hoop-size, include = T, echo = T, message = F, warning = F, cache = TRUE}
# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = HS_prior,
                    cores = 2,
                    chains = 2,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))

@@

``` {r HS_results, include = T, echo = T}
# Show fixed effects 
summary(Hoop_size_m1)$fixed
```

@@

``` {r PltHoopSize, include = T, echo = F, fig.asp = .45, fig.cap="_Figure on the left shows the Prior predictions. The figure on the right shows the Posterior predictions once the model had been conditioned on the data_"}
# get legend 
HoopSizeLegend <- g_legend(plt_prior_hoopsize)

grid.arrange(arrangeGrob(plt_prior_hoopsize + theme(legend.position = "none"), plt_post_hoopsize + theme(legend.position = "none"), ncol = 2),
             HoopSizeLegend, heights = c(10,1))
```
## Experiment 2: Two Throws

@@

# rename some variables for legibility
model_data_pos <- model_data_pos %>% 
  mutate(Num_throws = ifelse(Num_throws == "One-Throw", "One", "Two"))

source("extract_draws_functions/Two_throw_draws_noint.R")
```

@@

``` {r TwoThrowFacets, include = T, echo = F, fig.width = 10, fig.cap = "_Facet plots for each participant in the Two Throw experiment_"}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

```{r TwoThrowsParameters, include = F, echo = F}
TT_prior <- c(
  set_prior("student_t(4,0,.8)", class = "b", coef = "norm_delta"),
  set_prior("student_t(4,0,.8)", class = "b", coef = "norm_delta:Num_throwsTwo"),
  set_prior("student_t(4,0,.8)", class = "b", coef = "Num_throwsTwo"),
  set_prior("student_t(4,0,.8)", class = "b", coef = "Num_throwsOne"))

TT_iter = 100
TT_control = list(adapt_delta = .99, max_treedepth = 15)

```{r Two_Throws_Priors_only_model, include = F, echo = T, cache = T}
Two_throw_priors <- brm(
  abspos ~ 0 + norm_delta * Num_throws + (0 + norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = TT_prior,
  cores = 1,
  chains = 1,
  iter = TT_iter,
  warmup = TT_iter/2,
  control = TT_control,
  sample_prior = "only")
```

```{r PltTwoThrowPriors_setup, include = F, echo = F}
# get draws 
draws_df <- draw_post_delta(Two_throw_priors, model_data_pos)

priors_plt <- draws_df$Draws_df %>%
  mutate(prop = boot::inv.logit(estimate),
         Dist_type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(prop,colour = Num_throws, fill = Num_throws)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(expression(paste("Normalised ", Delta))) +
  geom_density(kernel = "biweight", alpha = .3) + 
  facet_wrap(~Dist_type) + 
  theme_bw() + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws")) +
  theme(legend.position = "bottom")

@@

Two_throw_m1 <- brm(
  abspos ~ 0 + norm_delta * Num_throws + (0 + norm_delta * Num_throws|Participant),
  family = "beta",
  data = model_data_pos,
  prior = TT_prior,
  cores = 1,
  chains = 1,
  iter = TT_iter,
  warmup = TT_iter/2,
  control = TT_control,)

@@

summary(Two_throw_m1)$fixed

@@

As can be seen from the summary output above, $\hat{R} \approx 1$.

```{r PltTwoThrowEstimates, include = F, echo = F}
# get draws
draws <- draw_post_delta(Two_throw_m1, model_data_pos)
# example distributions 
plt_examples <- draws$Plots[1][[1]][["data"]] %>% 
  mutate(Dist_Type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(prop, 
             colour = Num_throws,
             fill = Num_throws)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  facet_wrap(~Dist_Type) + 
  theme_bw() + 
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  coord_cartesian(expand = F) + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws")) +
  theme(legend.position = "bottom")

@@

# show this 
# gridExtra::grid.arrange(plt_examples, plt_difference)
```

```{r TwoThrowPlts, include = T, echo = F, fig.asp = .65, fig.cap = "_The left hand plots show the Prior preditcions for the Two Throw experiment. The right hand plots show the Posterior predictions for the Two Throw expeirment._"}
# get legend 
TwoThrowLegend <- g_legend(priors_plt)

grid.arrange(arrangeGrob(priors_plt + theme(legend.position = "none"), plt_examples + theme(legend.position = "none")),
                     TwoThrowLegend, heights=c(10, 1))

@@

This effect was the strongest for the closest separation which reflects the larger amount of variation in standing position with distance in the Two-throw condition (Figure \@ref(fig:TwoThrowPlts). In general, when in the One-throw condition, participants stood further from the centre (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) than in the the Two-throw condition (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) with P(One-throw > Two_throw|data) = `r paste(P_close$above0*100, "%", sep = "")`.

@@

source("extract_draws_functions/Reward_draws_noint.R")
```

@@

A Bayesian Beta Regression was carried out in order to investigate whether opting for an unequal reward structure in this task would facilitate the use of a more optimal strategy in the _Throwing Task_. The predictors in this model were whether the participant had opted for an _Equal_ or _Unequal_ (Gamble_Type), whether the hoops were _Close_ or _Far_ (dist_type), and the interaction between these. Additionally, random effects of participant were included for all predictors. The predicted value was the normalised standing position, with 0 representing the centre and 1 being next to one of the hoops.  
```{r RewardsParameters, echo = F, include = F}
R_prior <- c(set_prior("student_t(3,0,.5)",
                       class = "b",
                       coef = "dist_typefar"),
             set_prior("student_t(3,0,.5)",
                       class = "b",
                       coef = "dist_typefar:Gamble_TypeUnequal"),
             set_prior("student_t(3,0,.5)",
                       class = "b",
                       coef = "Gamble_TypeUnequal"),
             set_prior("student_t(3,0,.5)",
                       class = "b",
                       coef = "dist_typeclose"))

R_iter = 10000
R_control = list(adapt_delta = .99, max_treedepth = 15)

```{r GamblingPriorsOnly, include = F, echo = T, warning = F, cache = T}
Reward_priors <- brm(
  Norm_Dist ~ 0 + dist_type * Gamble_Type + (dist_type * Gamble_Type | Participant),
  data = model_data,
  family = "beta",
  prior = R_prior,
  chains = 1,
  iter = R_iter,
  warmup = R_iter/2,
  sample_prior = "only",
  control = R_control)
```

@@

```{r RewardModel, include = F, echo = T, warning = F, cache = T}
# run model 
Reward_m1 <- brm(
  Norm_Dist ~ 0 + dist_type * Gamble_Type + (dist_type * Gamble_Type | Participant),
  data = model_data,
  family = "beta",
  prior = R_prior,
  chains = 1,
  iter = R_iter,
  warmup = R_iter/2,
  control = R_control)

@@

## Note
This experiment was cut from the main body of the paper as it is the only experiment to make use of the _Detection Task_ from @clarke2015failure. The logic behind this experiment was the same as in the experiments discussed in the main paper in that we investigated a potential asymmetry in the design that may alter the way in which participants approached this task.

@@

plt_ProbPrior_meDist <- prior_draws %>%
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") +
  see::scale_color_material() + 
  see::scale_fill_material() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))
